Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2017-07-23 paper/paper.tex
Little changes

\jairheading{1}{2016}{0-0}{0/0}{0/0}
\ShortHeadings{Why Real-World Subgraph Matching is Easy}
{McCreesh, Prosser \& Trimble}
\firstpageno{1}

@@

\title{Why Real-World Subgraph Matching is Easy, and \\ What This Means for Filter / Verify in
Graph Databases \thanks{Part of this paper appeared at IJCAI
\citep{DBLP:conf/ijcai/McCreeshPT16}; \cref{section:introduction} has been expanded and
\cref{section:models,section:labelled,section:filterverify} are new material.}}

@@

For certain choices of parameters for induced isomorphisms, there are two phase transitions, going
from satisfiable to unsatisfiable, and then from unsatisfiable back to satisfiable. Again, when
going from satisfiable to unsatisfiable (from either direction), instances go from being trivial to
really hard to solve. However, each of the three solvers we tested also finds the central
unsatisfiable region to be hard, despite it not being near a phase transition. To show that this is
not a simple weakness of current subgraph isomorphism algorithms, we verify that this region is also
hard when using a pseudo-boolean encoding, and under reduction to the clique problem. Interestingly,
the constrainedness measure proposed by \citet{DBLP:conf/aaai/GentMPW96} \emph{does} predict this difficult
region---the third contribution of this paper is to use these instances to provide evidence in
favour of constrainedness, rather than proximity to a phase transition, being an accurate predictor
of difficulty, and to show that constrainedness is not simply a refinement of a phase transition
prediction.

>>>>

\jairheading{1}{2016}{0-0}{0/0}{0/0}
\ShortHeadings{Why Real-World Subgraph Isomorphism is Easy}
{McCreesh, Prosser \& Trimble}
\firstpageno{1}

@@

\title{Why Real-World Subgraph Isomorphism is Easy, and \\ What This Means for Filter / Verify in
Graph Databases \thanks{Part of this paper appeared at IJCAI
\citep{DBLP:conf/ijcai/McCreeshPT16}; \cref{section:introduction} has been expanded and
\cref{section:models,section:labelled,section:filterverify} are new material.}}

@@

For certain choices of parameters for induced isomorphisms, there are two phase transitions, going
from satisfiable to unsatisfiable, and then from unsatisfiable back to satisfiable. Again, when
going from satisfiable to unsatisfiable (from either direction), instances go from being trivial to
really hard to solve. However, each of the three solvers we test also finds the central
unsatisfiable region to be hard, despite it not being near a phase transition. To show that this is
not a simple weakness of current subgraph isomorphism algorithms, we verify that this region is also
hard for boolean satisfiability, pseudo-boolean, and mixed integer solvers, and under reduction to
the clique problem. Interestingly, the constrainedness measure proposed by
\citet{DBLP:conf/aaai/GentMPW96} \emph{does} predict this difficult region---the third contribution
of this paper is to use these instances to provide evidence in favour of constrainedness, rather
than proximity to a phase transition, being an accurate predictor of difficulty, and to show that
constrainedness is not simply a refinement of a phase transition prediction.
